Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-08-01 Latex/journal_v1/V5/pr.tex
read paper until proposed method

\section{Introduction} 
One of the fifth-generation goals of the wireless system is to achieve the desired QoS (such as rate, delay, power, ...) for different types of services. Network slicing is the best solution for this aim. A network slice is an end-to-end logical network that offers services with specific needs.  
Multiple isolated network slices run, manage, and work independently on the same infrastructure. 
Several implementations of network slicing include network core slicing, RAN slicing, and slicing of both sections. 
Different type of services includes enhanced mobile broadband (eMBB), and ultra-reliable low latency communications (URLLC), and massive Machine Type Communications (mMTC) services are introduced in 5th generation of mobile network. Each type of service requires a particular slice of network based on its QoS.
eMBB requires a higher transmission data rate in comparison with 4G systems. Moreover, eMBB service satisfies the demands of high capacity and considerable coverage.
URLLC requires low latency restrictions and higher reliability of the system.
URLLC contains services such as autonomous vehicles, tactile internet, or remote surgery.
mMTC consists of a vast number of low power Internet of Things (IoT) devices transmitting small payloads to a typical receiver. In addition, mMTC UEs include sensors for sensing, metering, and monitoring devices 
\cite{shen2020ai,setayesh2020joint,popovski20185g,dogra2020survey,kassab2018coexistence,alsenwi2021intelligent}.

Recently, RAN virtualization attracts significant attention from industry and academia since it has remarkable benefits that increase flexibility and reduce operating costs such as CAPEX and OPEX and allow them to add new capabilities to the network more quickly. In addition to RAN virtualization, openness and RAN intelligence are two other fundamental points that encourage the Open Radio Access Network (O-RAN) Alliance to establish O-RAN as the next generation of RAN systems.

The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both. CRAN divides RAN into two parts radio remote head (RRH) and baseband unit (BBU).  More than one distributed RRHs can be connected to a centralized BBU, which is named BBU-pool \cite{han2019research}. 
Unlike the previous generation of RAN that divides RAN into two parts, O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU). 
O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node that includes higher PHY, MAC, and RLC.
 In addition, the O-CU depicts the logical node contains two parts, which are the O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation,
RAN Intelligent Controller (RIC)- Near Real-Time and O-Cloud. 
One of the necessities of the new generation of wireless networks is its intelligence.
Based on the requirement of an intelligent wireless network, O-RAN offers machine learning techniques. The two logical nodes RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC- Near Real Time, implement the algorithms for network intelligence 
\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.

The separation of network software and hardware elements has been done and introduced as network function virtualization (NFV), and virtual network functions (VNF) are system function blocks. This technology improves the system performance in the fifth generation of telecommunications. 
The key idea of the implementation of NFV is to decouple software from physical hardware, dynamic scaling, and the deployment of flexible network functions. A usual NFV offer is to execute VNFs on virtual machines or containers in a cloud system \cite{mijumbi2015network, luo2020online}.
As a result, some O-RAN components that include user plane function (UPF), O-CU, O-DU, and RAN Intelligent Controller (RIC)-near real-time, are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
\subsection{Related Works}
Network slicing is increasingly receiving research attention.
Many researchers studied the problem of resource allocation in network slicing for multitenant cellular networks \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic}, dynamic network slicing in multitenant heterogeneous CRAN (H-CRAN) is considered. The process of allocating network resources to users is discussed. The network slicing scheme includes a higher level, which manages user acceptance control, user communication includes radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), the allocation of BBU capacity, and a lower level, which is the allocation of power and physical resource blocks (PRB) among us
In the article, \cite{xiang2020realization}, network slicing in the radio section is considered for fog or F-RAN structure, in which two network slices are set for hotspots and vehicle scenarios with related infrastructure. In \cite{elayoubi20195g,d2020toward} the implementation of RAN level slicing is discussed in mobile network operator (MNO). Also, the problem of resource allocation is considered.  Moreover, the challenges facing RAN slicing have also been explored, one of which involves designing and managing multiple slices in the shared infrastructure in an efficient manner while guaranteeing the agreed service level agreement (SLA) for each.

Multiplexing eMBB and URLLC services on the same RAN and sharing the resources for these services is challenging because many researchers pay attention to this topic.
In \cite{setayesh2020joint,yang2020should} the problem of resource allocation in the coexistence of these two services (URLLC and eMBB) is considered based on their QoS. 
In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC is formulated and solved by deep reinforcement learning.
 In \cite{saggese2021power} the problem of power minimization for these two types of services (URLLC and eMBB) is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA).
 In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services. The system guarantees the latency, the service rate, and the maintenance of reliability.

Virtualization technique for RAN and core is one of the exciting topics.  
In \cite{SystemCostMinimization,guo2016exploiting}, the authors solve the problem of obtaining beamforming and VMs activation in a C-RAN system with limited fronthaul capacity. 
This paper aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint. 
Also, Transmission and processing delay are modeled based on M/M/1 queuing theory to guarantee delay for the services.
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to UE is considered and solved using novel methods.
In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
\subsection{Main Contribution}
This study aims to optimize VNF activation, power allocation, PRB allocation, and O-RUs association to develop an isolated network slicing outline for different types of services in an O-RAN platform. In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follow:
\begin{itemize}
\item In this paper, a network slicing model is depicted for three different types of services introduced in 5G (URLLC, eMBB, and mMTC). The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for a different types of services with specific QoS. 
\item The desired QoS conditions such as delay and throughput are considered for different types of services. We formulate the end-to-end mean delay of the system based on the activated VNFs and each user's throughput.
We take into account the limited fronthaul capacity and accurately obtain the power and the capacity of each O-RU based on the quantization noise.
We model the interference of neighboring O-RU and formulate the actual throughput
for different types of services. We model the throughput of URLLC and mMTC based on their short packet transmission.
\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
We perform a two-step iterative algorithm to solve it.
The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\end{itemize}

@@

Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s}$ request from the single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2,3\}$ indicate service type).
There are different application requests which fall into one of these service categories. Each application request requires a specific QoS. Based on the application and QoS request, UE may be admitted and allocated to the resources.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of  preallocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.

All $K$ PRBs can be assigned to all UE in each service.
Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers. Each VM requires enough resources of CPU, memory, storage, and network bandwidth.

@@

\begin{equation}\label{eqI}
\begin{split}
I_{r,u(s,i)}^{k} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}_{r_j}^2 |\boldsymbol{h}_{r,{u(s,i)}}|^2 }_{\text{(Quantization Noise Interference)}}
\end{split}
\end{equation}
where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.\newline
$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.

To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal user $i$ in $s^{th}$ service
\begin{equation}\label{eq2}
\textstyle y_{u(s,i)} = \sum_{r = 1}^{R}\sum_{k=1}^{K_s} \boldsymbol{h}^{H \: k}_{r,u(s,i)} g_{u(s,i)}^r e^k_{r,u(s,i)}\mathfrak{y}^k_{r,u(s,i)}+ z_{u(s,i)},
\end{equation}
%\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}
where $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$
and $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }  $ indicates the quantization noise, which is made from signal compression in O-DU.

The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}$ that is formulated as below.
\begin{equation}\label{eq3}
\begin{split}
\mathcal{{R}}_{r,u(s_1,i)}^{k} &=  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}) ,\\
\mathcal{R}_{u(s_1,i)}^{r} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{r} g^r_{u(s_1,i)}
\end{split}
\end{equation}
where $B$ is the bandwidth of system. 
$\mathcal{R}_{u(s_1,i)}^{r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula. So, for the short packet transmission, the achievable data rate is approximated from following
\begin{equation}\label{eq11}
\begin{split}
\mathcal{{R}}_{r,u(s_j,i)}^{k} &= B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)}
\end{split}
\end{equation}
Where $j \in \{1,2\}$. Also we have
\begin{equation}\label{shortPacket}
 \zeta_{u(s_j,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})
\end{equation}
Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
$\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$, experiencing PRB $k$ and
$N_{u(s_j,i)}^{k}$ represents the blocklength of it. 
$\mathcal{R}_{u(s_j,i)}^{e,r}$ is the achievable rate of each O-RU $r$ to UE $i$ in slice $s_j$.

@@

P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q_r}^2.

@@

C_{r} = \log{(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q_{r}}^2})},

@@

Where, $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q_{r}}^2$ is the power of quantization noise.

@@

In this part, the end-to-end mean delay for a service is obtained.

@@

T_{tot} &=  T_{process} + T_{transmission} + T_{propagation}\\
T_{process} &=  T_{RU} + T_{DU} + T_{CU} + T_{UPF}\\
T_{transmission} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
T_{propagation} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\

@@

Total delay is the sum of processing delay, transmission delay, and propagation delay. 

@@

T_{tot} \approx T_{process}

@@

Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ slice.

@@

Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. since, by using Burke’s Theorem, the mean arrival data rate of the second and third layers, which are processed in the first layer, is still Poisson with rate $\alpha_{s}$

@@

T_{DU}^{s} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
T_{CU}^{s} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}}\\
T_{UPF}^{s} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}}\\

@@

$M_s^{u}$ are the variables that depict the sum of VNFs in O-DU, O-CU-UP and UPF, respectively. 

@@

T_{process}^{u(s,i)} =  T_{RU}^{u(s,i)} + T_{DU}^{s} + T_{CU}^{s} + T_{UPF}^{s}

@@

Hence, $T_{tot}^{u(s,i)} \approx T_{process}^{u(s,i)} $

@@

The optimization problem is formulated as follow.

>>>>

\section{Introduction} 
One of the fifth-generation goals of the wireless system is to achieve the desired QoS (such as rate, delay, power, ...) for different types of services. Network slicing is the best solution for this aim. A network slice is an end-to-end logical network that offers services with specific needs.  
Multiple isolated network slices run, manage, and work independently on the same infrastructure. 
Several implementations of network slicing include core slicing, RAN slicing, and slicing of both sections. 
Different type of services includes enhanced mobile broadband (eMBB), and ultra-reliable low latency communications (URLLC), and massive Machine Type Communications (mMTC) services are introduced in 5th generation of mobile network. Each type of service requires a particular slice of network based on its QoS.
eMBB requires a higher transmission data rate in comparison with 4G systems. Moreover, eMBB service satisfies the demands of high capacity and considerable coverage.
URLLC requires low latency restrictions and higher reliability of the system.
URLLC contains services such as autonomous vehicles, tactile internet, or remote surgery.
mMTC consists of a vast number of low power internet of ihings (IoT) devices transmitting small payloads to a typical receiver. In addition, mMTC UEs include sensors for sensing, metering, and monitoring devices 
\cite{shen2020ai,setayesh2020joint,popovski20185g,dogra2020survey,kassab2018coexistence,alsenwi2021intelligent}.

Recently, RAN virtualization attracts significant attention from industry and academia since it has remarkable benefits that increase flexibility and reduce operating costs such as CAPEX and OPEX and allow them to add new capabilities to the network more quickly. In addition to RAN virtualization, openness and RAN intelligence are two other fundamental points that encourage the Open Radio Access Network (O-RAN) Alliance to establish O-RAN as the next generation of RAN systems. 
The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both. CRAN divides RAN into two parts radio remote head (RRH) and baseband unit (BBU).  More than one distributed RRHs can be connected to a centralized BBU, which is named BBU-pool \cite{han2019research}. 
Unlike the previous generation of RAN that divides RAN into two parts, O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU). 
O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node that includes higher PHY, MAC, and RLC.
 In addition, the O-CU depicts the logical node contains two parts, which are the O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation,
RAN Intelligent Controller (RIC)- Near Real-Time and O-Cloud. 
One of the necessities of the new generation of wireless networks is its intelligence.
Based on the requirement of an intelligent wireless network, O-RAN offers machine learning techniques. The two logical nodes RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC- Near Real Time, implement the algorithms for network intelligence 
\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.

The separation of network software and hardware elements has been done and introduced as network function virtualization (NFV), and virtual network functions (VNF) are system function blocks. This technology improves the system performance in the fifth generation of telecommunications. 
The key idea of the implementation of NFV is to decouple software from physical hardware, dynamic scaling, and the deployment of flexible network functions. The NFV technology offers to execute VNFs on virtual machines or containers in a cloud system \cite{mijumbi2015network, luo2020online}.
As a result, some O-RAN components that include user plane function (UPF), O-CU, O-DU, and RAN Intelligent Controller (RIC)-near real-time, are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
\subsection{Related Works}
Network slicing is increasingly receiving research attention.
Many researchers studied the problem of resource allocation in network slicing for multitenant cellular networks \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic}, dynamic network slicing in multitenant heterogeneous CRAN (H-CRAN) is considered. The process of allocating network resources to users is discussed. The network slicing scheme includes a higher level and the lower level. The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), the allocation of BBU capacity. Also, in the lower level, the allocation of power and physical resource blocks (PRB) is performed.
In the article \cite{xiang2020realization}, network slicing in the radio section is considered for fog or F-RAN structure, in which two network slices are set for hotspots and vehicle scenarios with related infrastructure. In \cite{elayoubi20195g,d2020toward} the implementation of RAN level slicing is discussed in mobile network operator (MNO). Also, the problem of resource allocation is considered. Moreover, the paper faces the challenge of RAN slicing. The problem involves designing and managing multiple slices in the shared infrastructure efficiently while guaranteeing each slice's service level agreement (SLA).

Multiplexing eMBB and URLLC services on the same RAN and sharing the resources of these services is challenging, and many researchers pay attention to this issue.
In \cite{setayesh2020joint,yang2020should} the problem of resource allocation in the coexistence of URLLC and eMBB services is considered based on their QoS. 
In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC services is formulated and solved by deep reinforcement learning.
 In \cite{saggese2021power} the problem of power minimization for URLLC and eMBB services is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA).
 In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services. The system guarantees the latency, the service rate, and the maintenance of reliability.

Virtualization technique for RAN and core is one of the exciting topics.  
In \cite{SystemCostMinimization,guo2016exploiting}, the authors solve the problem of obtaining beamforming and VMs activation in a C-RAN system with limited fronthaul capacity. 
This paper aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint. 
Also, transmission and processing delay are modeled based on M/M/1 queuing theory to guarantee delay for the UEs.
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to the UE is considered and solved using innovative methods.
In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
\subsection{Main Contribution}
This study aims to optimize baseband resource allocation (power allocation, PRB allocation, and O-RUs association) and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform. In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follow:
\begin{itemize}
\item In this paper, a network slicing model is depicted for three different types of services introduced in 5G (URLLC, eMBB, and mMTC). The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for a different types of services with specific QoS. 
\item The desired QoS conditions such as delay and throughput are considered for different types of services. We formulate the end-to-end mean delay of the system based on the number of activated VNFs and each user's throughput.
We consider the limited fronthaul capacity and accurately obtain the power and the capacity of each O-RU based on the quantization noise.
We model the interference of neighboring O-RU and formulate the actual throughput
for different types of services. We model the throughput of URLLC and mMTC based on their short packet transmission.
\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
We perform a two-step iterative algorithm to solve it.
The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\end{itemize}

@@

Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ request from the single-antenna UEs which require certain QoS to be able to use the requested service ($j \in \{1,2,3\}$ indicate service type).
There are different application requests which fall into one of these service categories. Each application request requires a specific QoS. Based on the application and QoS request, UE may be admitted and allocated to the resources.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2\}$ consists of  preallocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.

All $K$ PRBs can be assigned to all UE in each service.
Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers.

@@

\begin{equation}\label{eqI}
\begin{split}
I_{r,u(s,i)}^{k} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}|^2 }_{\text{(Quantization Noise)}}
\end{split}
\end{equation}
where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU.

To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service
\begin{equation}\label{eq2}
\textstyle y_{u(s,i)} = \sum_{r = 1}^{R}\sum_{k=1}^{K_s} \boldsymbol{h}^{H \: k}_{r,u(s,i)} g_{u(s,i)}^r e^k_{r,u(s,i)}\mathfrak{y}^k_{r,u(s,i)}+ z_{u(s,i)},
\end{equation}
%\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}
where $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$
and $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }  $ indicates the quantization noise 
($\boldsymbol{q}_{r} \backsim \mathcal{N}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$), which is made from signal compression in O-DU.

The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}$ that is formulated as below.
\begin{equation}\label{eq3}
\begin{split}
\mathcal{{R}}_{r,u(s_1,i)}^{k} &=  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}) ,\\
\mathcal{R}_{u(s_1,i)}^{r} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{r} g^r_{u(s_1,i)}
\end{split}
\end{equation}
where $B$ is the bandwidth of system. 
$\mathcal{R}_{u(s_1,i)}^{r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula. So, for the short packet transmission, the achievable data rate is approximated from following
\begin{equation}\label{eq11}
\begin{split}
\mathcal{{R}}_{r,u(s_j,i)}^{k} &= B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)}
\end{split}
\end{equation}
Where $j \in \{2,3\}$. Also we have
\begin{equation}\label{shortPacket}
 \zeta_{u(s_j,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})
\end{equation}
Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
$\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$, experiencing PRB $k$ and
$N_{u(s_j,i)}^{k}$ represents the blocklength of it. 
$\mathcal{R}_{u(s_j,i)}^{e,r}$ is the achievable data rate that is transmitted by O-RU $r$ to UE $i$ requesting service $s_j$.

@@

P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q}^2.

@@

C_{r} = \log{(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q}^2})},

@@

Where, $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q}^2$ is the power of quantization noise.

@@

In this part, the end-to-end mean delay for each service is obtained.

@@

T^{tot} &=  T^{process} + T^{transmission} + T^{propagation}\\
T^{process} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF}\\
T^{transmission} &= T^{front} + T^{mid} + T^{back} + T^{trans2net} \\
T^{propagation} &= T^{front} + T^{mid} + T^{back} + T^{trans2net} \\

@@

The total delay ($T^{tot}$) is the sum of the processing delay ($T^{process}$), the transmission delay ($T^{transmission}$), and the propagation delay($T_{propagation}$). 

@@

T^{tot} \approx T^{process}

@@

Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ service (or slice).

@@

Assume the mean arrival data rate of the UPF layer for the slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$). so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$,
Because the amount of data traffic transferred along the route (regardless of frame changes) is constant.
Since, by using Burke’s theorem, the mean arrival data rate of the second and third layers, which are processed in the first layer, is still poisson with rate $\alpha_{s}$.

@@

T_{s}^{DU} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
T_{s}^{CU} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}}\\
T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}}\\

@@

$M_s^{u}$ are the variables that depict the number of VNFs in O-DU, O-CU-UP and UPF, respectively. 

@@

T^{process}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}

@@

Hence, $T^{tot}_{u(s,i)} \approx T^{process}_{u(s,i)} $

@@
